Re-run, Repeat, Reproduce, Reuse, Replicate:\\Transforming Code into Scientific Contributions

### 2017-10-19 draft.tex
insisting

Replicability\footnote{\emph{Reproducibility} and \emph{replicability} are employed differently by different authors and in different domains (see for instance the report from the U.S.  \cite{Schwalbe:2016}). Here, we place ourselves in the context of computational works, where data is produced by a program. A result is \emph{reproducible} if one can take the original source code, re-execute it and reobtain the original results. A result is \emph{replicable} if one can create a code that matches the algorithmic descriptions given in the published article and reobtain the original results.} is a cornerstone of science.  If an experimental result cannot be
re-obtained by an independent party, it merely becomes, at best, an observation
that may inspire future research \citep{Mesirov:2010,osc:2015}. Replication
issues have received increased attention in recent years, with a particular focus on medicine and psychology \citep{Iqbal:2016}. One could think
that computational research would mostly be shielded from such issues, since a
computer program describes precisely what it does and is easily
disseminated to other researchers without alteration.

@@

Code is an central part of a submission to the ReScience journal. During the review process, reviewers run the submitted code, may criticise its quality and its ease-of-use, and verify the reproduciblity of the replication. The Journal of Open Source Software \citep{Smith:2017} functions similarly: testing the code is a fundamental part of the review process.

>>>>

Replicability\footnote{\emph{Reproducibility} and \emph{replicability} are employed differently by different authors and in different domains (see for instance the report from the U.S.  \cite{Schwalbe:2016}). Here, we place ourselves in the context of computational works, where data is produced by a program. In this paper, we call a result \emph{reproducible} if one can take the original source code, re-execute it and reobtain the original results. Conversely, a result is \emph{replicable} if one can create a code that matches the algorithmic descriptions given in the published article and reobtain the original results.} is a cornerstone of science.  If an experimental result cannot be
re-obtained by an independent party, it merely becomes, at best, an observation
that may inspire future research \citep{Mesirov:2010,osc:2015}. Replication
issues have received increased attention in recent years, with a particular focus on medicine and psychology \citep{Iqbal:2016}. One could think
that computational research would mostly be shielded from such issues, since a
computer program describes precisely what it does and is easily
disseminated to other researchers without alteration.

@@

Code is a key part of a submission to the ReScience journal. During the review process, reviewers run the submitted code, may criticise its quality and its ease-of-use, and verify the reproduciblity of the replication. The Journal of Open Source Software \citep{Smith:2017} functions similarly: testing the code is a fundamental part of the review process.
